Technical Report

### 2018-03-21 fully-abstract-comp/technical-report.tex
Modify convention about seal locations
In more detail:
* call now takes an offset saying where the seal can be found relative to the pc
* components can now put seals everywhere they want, not just at the start of their
  code

Reason: makes linking easier, simpler overall.

The source machine is also a capability machine with memory capabilities and sealed capabilities. Unlike the target machine, the source machine has a built in stack along with special stack and return tokens used in place of the actual capabilities. The syntax of the source machine language is as follows:
\[
  \begin{array}{rcl}
    o & \in & \nats \\
    \src{i} & \defbnf &  \trg{i} \mid \scall{o}{r}{r}
  \end{array}
\]
There is one syntactic difference between the source language and the target language, namely the target language has an extra instruction in the $\scall{o}{}{}$ instruction (the $o$ refers to the seal it uses, namely the offset in the seals made available by linking).

The source machine allows for variable length instructions which we utilise for $\scall{o}{}{}$. In other words, when $\scall{o}{}{}$ is decoded, a series of addresses in memory must contain what corresponds to the call instruction (and be within the range of the pc capability). This is described in more detail when we present the decoding function.

@@

\paragraph{Step relation}
The instruction $\scall{o}{}{}$ has length $\calllen$ which means that it does not fit in one memory address. In fact, $\scall{o}{}{}$ should be seen as a different way of interpreting a series of instruction rather than an instruction on its own. We therefore introduce $\scall[0]{o}{r_1}{r_2},\dots,\scall[\calllen-1]{o}{r_1}{r_2}$ as aliases for the instructions that constitute $\scall{o}{r_1}{r_2}$ (see Paragraph~\ref{par:call-impl} for details). We define the following condition that indicates that $\aaddr$ is the first address of a $\scall{o}{r_1}{r_2}$ instruction in the configuration $\Phi$:
\[
  \sourcecolor\left.
    \callCond{\Phi,r_1,r_2,\aaddr} = \left\{
      \begin{array}{l}
        \Phi.\mem(\aaddr) = \scall[0]{o}{r_1}{r_2} \tand\\
        \vdots \\
        \Phi.\mem(\addr+\calllen-1) = \scall[\calllen-1]{o}{r_1}{r_2}
      \end{array}
      \right.
  \right.
\]

@@

\begin{align*}
  \src{\Phi} & \; \src{\step \sem{\scall{o}{r_1}{r_2}}(\Phi)} &  &\sourcecolor\left.\arraycolsep=0pt
                                                  \begin{array}[t]{l}
                                                    \text{if }\Phi(\pcreg) 
= ((\perm,\_),\baddr,\eaddr,\aaddr) \tand \\
                                                    \callCond{\Phi,r_1,r_2,\aaddr} \tand\\
                                                    \lbrack \aaddr ,\baddr \rbrack \subseteq \ta \tand \\
                                                    \baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr \tand \\
                                                    \exec{\Phi(\pcreg)}
                                                  \end{array}\right.\\
  \Phi & \step \sem{\decInstr{\Phi.\mem(\aaddr)}}(\Phi) & &\left.\arraycolsep=0pt
                                                  \begin{array}[t]{l}
                                                    \text{if }\Phi(\pcreg) = ((\perm,\_),\baddr,\eaddr,\aaddr) \tand \\
                                                    \src{(\neg\callCond{\Phi,r_1,r_2,\aaddr} \tor}\\
                                                    \src{\eaddr < \aaddr + \calllen-1) \tand} \\
                                                    \withinBounds{\Phi(\pcreg)} \tand \\
                                                    \exec{\Phi(\pcreg)}
                                                  \end{array}\right.\\
  \Phi& \step \failed & & \totherwise
\end{align*}
\dominique{Note: The above does not allow executing code that is on the stack in the source machine, while this is in principle allowed in the target.
This is probably fine if we make sure a stack pointer can never be executable.}

@@

\paragraph{Call implementation}
\label{par:call-impl}
This paragraph contains the implementation of $\scall{o}{}{}$. That is each of the instructions in the implementation corresponds to $\scall[1]{o}{r_1}{r_2} \dots \scall[\calllen-1]{o}{r_1}{r_2}$, respectively.

%\lau{16-10-2017: Fill this paragraph with $\scall{o}{}{}$ implementation, i.e., the instructions $\scall[1]{o}{r_1}{r_2} \dots \scall[\calllen]{o}{r_1}{r_2}$ is equal to. Add convenience notation like $\update{\mem.a}{\scall{o}{r_1}{r_2}} = \dots$}
\lau{16-10-2017: Implementation of $\scall{o}{}{}$ may need registers for temporary registers - we should update the semantics accordingly.}

@@

    \tsetatob{\rtmp{1}}\\

@@

    \tcca{\rtmp{1}}{o}\text{ // $o$ is the offset this call uses.}\\

@@

\dominique{It is a bit annoying that we store the stack end address before invocation if we do not use it.
  I understand this is for ensuring that our private stack frame is not empty, which is important.
  But why don't we just push a constant then?
  Also: perhaps we could only do it if the current private stack frame is empty to begin with?
}
\dominique{4-12-2017: update: Lau executed the first suggestion (push a constant instead), and convinced me that the last suggestion didn't make sense (only push if the current private stack is empty), because it is then not clear whether or not to pop in the return code.}

@@

For convenience, we will add the convention that the memory update $\update{\mem.a}{\scall{o}{r_1}{r_2}}$ corresponds to
\[
  \begin{array}{l}
    \update{\mem.a}{\scall[0]{o}{r_1}{r_2}}\\
    \update{\mem.a+1}{\scall[1]{o}{r_1}{r_2}}\\
    \dots\\
    \update{\mem.a+\calllen-1}{\scall[\calllen-1]{o}{r_1}{r_2}}\\
  \end{array}
\]

@@

  \sem{\scall{o}{\src{r_1}}{\src{r_2}}}(\Phi) = & 

@@

                                                   \mem(\baddr) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\aaddr}\tand\\
                                                   \sigma_? = \sigma_\aaddr + o \tand\\

@@

\subsection{Program layout and linking}
A target-level program needs a number of things available in order to be able to execute securely. In the following, we list what it needs followed by a description of how they are made available.

@@

We define a component as follows:
\begin{align*}
  \var{comp} &\mathrel{::=} (\ms_{\mathrm{code}},\ms_{\mathrm{data}},\overline{c}_{\mathrm{import}},\overline{c}_{\mathrm{export}},\sigma_\baddr,\nrcalls,\nrclosures)
\end{align*}

We define inductively when a component is valid ($\vdash \var{comp}$) by the below inference rules:
\begin{mathpar}
  \inference{}{
    A_{\mathrm{code}},A_{\mathrm{data}},\overline{c_{\mathrm{import}}},\sigma_\baddr,\nrcalls,\nrclosures \vdash_{\mathrm{comp-value}} z
  }
  \and
  \inference{
    c \in \overline{c_{\mathrm{import}}}
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigma_\baddr,\nrcalls,\nrclosures \vdash_{\mathrm{comp-value}} c
  }
  \and
  \inference{
    [\baddr,\eaddr] \subseteq A_{\mathrm{code}} & \perm \sqsubseteq \rx
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigma_\baddr,\nrcalls,\nrclosures \vdash_{\mathrm{comp-value}} ((\perm,\normal),\baddr,\eaddr,\aaddr)
  }
  \and
  \inference{
    [\baddr,\eaddr] \subseteq A_{\mathrm{data}} & \permbnf \sqsubseteq \rw&
    \lin = \linear \Rightarrow \emptyset \subset [\baddr,\eaddr] \subseteq A_{\mathrm{own}}
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigma_\baddr,\nrcalls,\nrclosures \vdash_{\mathrm{comp-value}} ((\perm,\lin),\baddr,\eaddr,\aaddr)
  }
  \and
  \inference{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigma_\baddr,\nrcalls,\nrclosures \vdash_{\mathrm{comp-value}} \vsc \\
    \sigma = \sigma_b + o & \nrcalls \leq o < \nrcalls + \nrclosures
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigma_\baddr,\nrcalls,\nrclosures \vdash_{\mathrm{comp-value}} \sealed{\sigma,\vsc}
  }
  \and
  \inference{
    \dom(\ms_{\mathrm{code}}) = [\baddr_{\mathrm{code}},\eaddr_{\mathrm{code}}] &
    \ms_{\mathrm{code}}(\baddr_{\mathrm{code}}) = \seal{\sigma_\baddr,\sigma_\baddr+\nrcalls+\nrclosures-1,\sigma_\baddr}\\
    \forall a \in [\baddr_{\mathrm{code}}+1,\eaddr_{\mathrm{code}}]\ldotp \ms_{\mathrm{code}}(a) \in \ints\\
    \exists \var{offset\_use\_site} \in [0\cdots \nrcalls-1] \fun \dom(\ms_{\mathrm{code}}) \\
    \forall a \in [\baddr_{\mathrm{code}}+1,\eaddr_{\mathrm{code}}-\calllen+1]\ldotp \ms_{\mathrm{code}}([a\cdots a+\calllen-1]) = \scall[0..\calllen-1]{o}{r_1}{r_2} \Rightarrow \var{offset\_use\_site}(o) =a\\
    \exists A_\mathrm{own} : \dom(\ms_{\mathrm{data}}) \rightarrow \powerset{\dom(\ms_{\mathrm{data}})} & \dom(\ms_{\mathrm{data}}) = \biguplus_{a \in \dom(\ms_{\mathrm{data}})} A_{\mathrm{own}}(a) \\
    \forall a \in \dom(\ms_{\mathrm{data}})\ldotp \dom(\ms_{\mathrm{code}}),\dom(\ms_{\mathrm{data}}),A_{\mathrm{own}}(a),\overline{c_{\mathrm{import}}},\sigma_\baddr,\nrcalls,\nrclosures \vdash_{\mathrm{comp-value}}\ms_{\mathrm{data}}(a)\\
    \overline{\dom(\ms_{\mathrm{code}}), \dom(\ms_{\mathrm{data}}), \emptyset, \overline{c_{\mathrm{import}}}, \sigma_\baddr, \nrcalls, \nrclosures \vdash_{\mathrm{comp-value}} c_{\mathrm{export}}}
  }{
    \vdash (\ms_{\mathrm{code}},\ms_{\mathrm{data}},\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigma_\baddr,\nrcalls,\nrclosures)
  }
\end{mathpar}

@@

\[
  \comp{\scall{o}{r_1}{r_2}} = 
  \begin{array}[t]{l}
    % Make the stack capability into the return capability and seal it:
    %   Push r_data to the stack (should this be made the responsibility of the programmer? If it happens here, then it should probably also be part of the call semantics. Especially, the call semantics should "eat" another piece of memory on the stack to make sure there is no discrepancy.)
    %   Seal the stack capability (with what? where does the seal come from? I think we talked about this, and it is something that should be handled like linking (a fresh seal is available in the beginning of a programs code along with a capability for a linking table)).
    % restrict the stack capability to the unused part (and clear this part (is this really necessary?)).
    % make return capability and ceal it:
    %   Move a copy of pc to a different register.
    %   Adjust the pc copy to point to the return address.
    %   Seal it with the seal.
    % remove all data from temp registers (that is at least the seal).
    % jmpx to r1 and r2
    % restore code:
    %   check the stack end address.
    %   move the stack pointer to the proper register
    %   pop the data capability
  \end{array}
\]

@@

\[
  \codereg{\ta,\sigma_\baddr,\nrcalls,\nrclosures,\code} \defeq (\pure,*,=,=,H^\mathrm{code} \; \ta \; \sigma_\baddr \; \nrcalls \; \nrclosures \; \code,H^\mathrm{code}_\sigma \; \ta \; \sigma_\baddr \; \nrcalls \nrclosures \; \code)
\]

\begin{multline*}
  H^\mathrm{code} \; \ta \; \sigma_\baddr \; \nrcalls \; \nrclosures \; \code \; s \; \hat{W} = \\\left\{
    \npair{(\code,\code)} \middle|
  \begin{multlined}
    \dom(\code) = [\aaddr,\baddr] \tand \sigma_\eaddr = \sigma_\baddr + \nrcalls+\nrclosures - 1 \tand \\
    \code(a) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr}
  \end{multlined}
  \right\}
\end{multline*}

\lau{19-03-2018: Add the link capability to the above? code in ta?}
\begin{multline*}
  H^\mathrm{code}_\sigma \; \ta \; \sigma_\baddr \; \nrcalls \; \nrclosures \; \code \; s \; \sigma \; \hat{W} = \\
  \begin{array}[t]{l}
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\retptrc(\rx,\lin,\baddr,\eaddr,\aaddr'+\calllen - 1),\\((\rx,\lin),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \decInstr{\code([a',a' + \calllen-1])} = \overline{\scall{o}{r_1}{r_2}} \tand \\
        \aaddr = \aaddr' + \retoffset \tand \\
        \sigma = \sigma_\baddr + o \tand o < \nrcalls\\
        \lbrack \baddr, \eaddr \rbrack = \dom(\code) \subseteq \ta
      \end{array}
    \end{array}
      \right\} \uplus \\
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\retptrd(\baddr,\eaddr),\\((\rw,\linear),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \exists r \in \dom(\pwpriv[\xi(\hat{W})]) \ldotp \pwpriv[\xi(\hat{W})](r) \nequal (\stareg[(\ms,\ms)]{\spa}, ((\rx,\lin),\baddr',\eaddr',\aaddr'+\calllen)) \tand \\
        \quad \dom(\ms) = [\baddr,\eaddr] \tand\\
        \quad \decInstr{\code([a',a' + \calllen-1])} = \overline{\scall{o}{r_1}{r_2}} \tand \\
        \quad \sigma = \sigma_\baddr + o \tand o < \nrcalls \tand\\
        \quad a = b-1\tand \\
        \quad \lbrack \baddr', \eaddr' \rbrack = \dom(\code) \subseteq \ta
      \end{array}
    \end{array}
      \right\} \uplus\\
    \left\{
    \begin{array}{l}
\left. \npair{(\vsc, \vsc' )} \middle| \right. \\
      \begin{array}{l}
        \sigma = \sigma_\baddr + o \tand \nrcalls \leq o < \nrcalls + \nrclosures \tand\\
        (\dom(\code) \mathrel{\#} \ta \tand \npair{(\vsc,\vsc')} \in \lrv \; W) \tor\\
        (\dom(\code) \subseteq \ta \tand \npair{(\vsc,\vsc')} \in \lrvtrusted \; W)
      \end{array}
    \end{array}
      \right\}
  \end{array}
\end{multline*}

@@

We want to make a conditional full-abstraction statement. The condition should express two things (1) the compilation so far has been reasonable, so we do not have to setup protection against things any reasonable compiler wouldn't do. (2) the compilation so far has taken care of certain checks that we do not have information to place correctly at this point of the compilation
\begin{definition}
  \label{def:check-stack-addr-before-call}
  A configuration $\src{\Phi}$ is said to have reasonable calls in $\ta$ for $n$ steps iff\\
  for all $i \leq n$ if
  \[
    \src{\Phi} \nstep[i] \src{\Phi'}
  \]
  and $\src{\Phi'}$ points to $\src{\scall{o}{r_1}{r_2}}$ in $A$ for some $\src{r_1}$ and $\src{r_2}$
  % and there exists no $j<i$ s.t.
  % \[
  %   \src{\Phi} \nstep[j] \src{\Phi''}
  % \]
  % where $\src{\Phi''}$ points to $\src{\scall{o}{r_1'}{r_2'}}$ in $A$ for some $\src{r_1'}$ and $\src{r_2'}$,
  then
  \[
    \src{\Phi'}(\src{r_\stk}) = \src{\stkptr{\_,\stkb,\_,\_}}
  \]
  % and $\src{\Phi'}$ has reasonable calls in $A$ for $n-i$ step.
\end{definition}

\begin{definition}[Use return seals only for call]
  A configuration $\src{\Phi}$ is said to use linker seals properly in $\ta$ for $n$ steps iff\\
  for all $i \leq n$, if
  \[
    \src{\Phi} \nstep[i] \src{\Phi'}
  \]
  and $\src{\Phi'}$ points to $\src{\tcseal{r_1}{r_2}}$ in $\ta$ and $\Phi'(r_1) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$, then either $\src{\Phi'}$ is inside $\src{\scall{o}{r_1'}{r_2'}}$ and $\sigma_\baddr \leq \sigma < \sigma_\baddr + \nrcalls$ or $\sigma_\baddr + \nrcalls \leq \sigma < \sigma_\baddr + \nrcalls + \nrclosures$.
\end{definition}

>>>>

The source machine is also a capability machine with memory capabilities and sealed capabilities. Unlike the target machine, the source machine has a built in stack along with special stack and return tokens used in place of the actual capabilities. The syntax of the source machine language is as follows:
\[
  \begin{array}{rcl}
    o & \in & \nats \\
    \src{i} & \defbnf &  \trg{i} \mid \scall{\offpc,\offsigma}{r}{r}
  \end{array}
\]
There is one syntactic difference between the source language and the target language, namely the target language has an extra instruction in the $\scall{\offpc,\offsigma}{}{}$ instruction (the $o$ refers to the seal it uses, namely the offset in the seals made available by linking).

The source machine allows for variable length instructions which we utilise for $\scall{\offpc,\offsigma}{}{}$. In other words, when $\scall{\offpc,\offsigma}{}{}$ is decoded, a series of addresses in memory must contain what corresponds to the call instruction (and be within the range of the pc capability). This is described in more detail when we present the decoding function.

@@

\paragraph{Step relation}
The instruction $\scall{\offpc,\offsigma}{}{}$ has length $\calllen$ which means that it does not fit in one memory address. In fact, $\scall{\offpc,\offsigma}{}{}$ should be seen as a different way of interpreting a series of instruction rather than an instruction on its own. We therefore introduce $\scall[0]{\offpc,\offsigma}{r_1}{r_2},\dots,\scall[\calllen-1]{\offpc,\offsigma}{r_1}{r_2}$ as aliases for the instructions that constitute $\scall{\offpc,\offsigma}{r_1}{r_2}$ (see Paragraph~\ref{par:call-impl} for details). We define the following condition that indicates that $\aaddr$ is the first address of a $\scall{\offpc,\offsigma}{r_1}{r_2}$ instruction in the configuration $\Phi$:
\[
  \sourcecolor\left.
    \callCond{\Phi,r_1,r_2,\aaddr} = \left\{
      \begin{array}{l}
        \Phi.\mem(\aaddr) = \scall[0]{\offpc,\offsigma}{r_1}{r_2} \tand\\
        \vdots \\
        \Phi.\mem(\addr+\calllen-1) = \scall[\calllen-1]{\offpc,\offsigma}{r_1}{r_2}
      \end{array}
      \right.
  \right.
\]

@@

\begin{align*}
  \src{\Phi} & \; \src{\step \sem{\scall{\offpc,\offsigma}{r_1}{r_2}}(\Phi)} &  &\sourcecolor\left.\arraycolsep=0pt
                                                  \begin{array}[t]{l}
                                                    \text{if }\Phi(\pcreg) 
= ((\perm,\_),\baddr,\eaddr,\aaddr) \tand \\
                                                    \callCond{\Phi,r_1,r_2,\aaddr} \tand\\
                                                    \lbrack \aaddr ,\baddr \rbrack \subseteq \ta \tand \\
                                                    \baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr \tand \\
                                                    \exec{\Phi(\pcreg)}
                                                  \end{array}\right.\\
  \Phi & \step \sem{\decInstr{\Phi.\mem(\aaddr)}}(\Phi) & &\left.\arraycolsep=0pt
                                                  \begin{array}[t]{l}
                                                    \text{if }\Phi(\pcreg) = ((\perm,\_),\baddr,\eaddr,\aaddr) \tand \\
                                                    \src{(\neg\callCond{\Phi,r_1,r_2,\aaddr} \tor}\\
                                                    \src{\eaddr < \aaddr + \calllen-1) \tand} \\
                                                    \withinBounds{\Phi(\pcreg)} \tand \\
                                                    \exec{\Phi(\pcreg)}
                                                  \end{array}\right.\\
  \Phi& \step \failed & & \totherwise
\end{align*}
\dominique{Note: The above does not allow executing code that is on the stack in the source machine, while this is in principle allowed in the target.
This is probably fine if we make sure a stack pointer can never be executable.}

@@

\paragraph{Call implementation}
\label{par:call-impl}
This paragraph contains the implementation of $\scall{\offpc,\offsigma}{}{}$. That is each of the instructions in the implementation corresponds to $\scall[1]{\offpc,\offsigma}{r_1}{r_2} \dots \scall[\calllen-1]{\offpc,\offsigma}{r_1}{r_2}$, respectively.

%\lau{16-10-2017: Fill this paragraph with $\scall{\offpc,\offsigma}{}{}$ implementation, i.e., the instructions $\scall[1]{\offpc,\offsigma}{r_1}{r_2} \dots \scall[\calllen]{\offpc,\offsigma}{r_1}{r_2}$ is equal to. Add convenience notation like $\update{\mem.a}{\scall{\offpc,\offsigma}{r_1}{r_2}} = \dots$}
\lau{16-10-2017: Implementation of $\scall{\offpc,\offsigma}{}{}$ may need registers for temporary registers - we should update the semantics accordingly.}

@@

    \tcca{\rtmp{1}}{\offpc} \text{ // $\offpc$ is the offset from pc to the location of the seal for this code}\\

@@

    \tcca{\rtmp{1}}{\offsigma}\text{ // $\offsigma$ is the offset for the seal used by this call.}\\

@@

% \dominique{It is a bit annoying that we store the stack end address before invocation if we do not use it.
%   I understand this is for ensuring that our private stack frame is not empty, which is important.
%   But why don't we just push a constant then?
%   Also: perhaps we could only do it if the current private stack frame is empty to begin with?
% \dominique{4-12-2017: update: Lau executed the first suggestion (push a constant instead), and convinced me that the last suggestion didn't make sense (only push if the current private stack is empty), because it is then not clear whether or not to pop in the return code.}

@@

For convenience, we will add the convention that the memory update $\update{\mem.a}{\scall{\offpc,\offsigma}{r_1}{r_2}}$ corresponds to
\[
  \begin{array}{l}
    \update{\mem.a}{\scall[0]{\offpc,\offsigma}{r_1}{r_2}}\\
    \update{\mem.a+1}{\scall[1]{\offpc,\offsigma}{r_1}{r_2}}\\
    \dots\\
    \update{\mem.a+\calllen-1}{\scall[\calllen-1]{\offpc,\offsigma}{r_1}{r_2}}\\
  \end{array}
\]

@@

  \sem{\scall{\offpc,\offsigma}{\src{r_1}}{\src{r_2}}}(\Phi) = & 

@@

                                                   \mem(a+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\aaddr}\tand\\
                                                   \sigma_? = \sigma_\aaddr + \offsigma \tand\\

@@

\subsection{Component layout and linking}
We define a notion of

A target-level program needs a number of things available in order to be able to execute securely. In the following, we list what it needs followed by a description of how they are made available.

@@

We define a component as follows:
\begin{align*}
  \var{comp} &\mathrel{::=} (\ms_{\mathrm{code}},\ms_{\mathrm{data}},\overline{c}_{\mathrm{import}},\overline{c}_{\mathrm{export}},\sigrets,\sigcloss)
\end{align*}

We define inductively when a component is valid ($\vdash \var{comp}$) by the below inference rules:
\begin{mathpar}
  \inference{
    \mscode(a) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\aaddr} & [\sigma_\baddr,\sigma_\eaddr] \subseteq (\sigrets \cup \sigcloss)
  }{
    \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \mscode,a
  }
  \and
  \inference{
    \mscode(a) \in \ints\\
    \mscode([a \cdots a + \calllen-1]) = \scall[0..\calllen-1]{\offpc,\offsigma}{r_1}{r_2} \Rightarrow (\mscode(a+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\aaddr} \wedge \sigma_\baddr+\offsigma \in \sigrets)
  }{
    \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \mscode,a
  }
  \and
  \inference{
    \exists d_\sigma : \dom(\mscode) \rightarrow \powerset{\Seal} \ldotp
    \sigrets = \biguplus_{a \in \dom(\mscode)} d_\sigma(a) \tand\\
    \forall a \in \dom(\mscode) \ldotp 
    d_\sigma(a),\sigcloss \vdash_{\mathrm{comp-code}} \mscode,a
  }{
    \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \mscode
  }
  \and
  \inference{
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} z
  }
  \and
  \inference{
    c \in \overline{c_{\mathrm{import}}}
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} c
  }
  \and
  \inference{
    [\baddr,\eaddr] \subseteq A_{\mathrm{code}} & \perm \sqsubseteq \rx
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} ((\perm,\normal),\baddr,\eaddr,\aaddr)
  }
  \and
  \inference{
    [\baddr,\eaddr] \subseteq A_{\mathrm{data}} & \permbnf \sqsubseteq \rw&
    \lin = \linear \Rightarrow \emptyset \subset [\baddr,\eaddr] \subseteq A_{\mathrm{own}}
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} ((\perm,\lin),\baddr,\eaddr,\aaddr)
  }
  \and
  \inference{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} \vsc \\
    \sigma \in \sigcloss
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} \sealed{\sigma,\vsc}
  }
  \and
  \inference{
    \dom(\mscode) \mathrel{\#} \dom(\msdata)\\
    \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \mscode \\
    \exists A_\mathrm{own} : \dom(\msdata) \rightarrow \powerset{\dom(\msdata)} & \dom(\msdata) = \biguplus_{a \in \dom(\msdata)} A_{\mathrm{own}}(a) \\
    \forall a \in \dom(\msdata)\ldotp \dom(\mscode),\dom(\msdata),A_{\mathrm{own}}(a),\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash \msdata(a)\\
    \overline{\dom(\mscode), \dom(\msdata), \emptyset, \overline{c_{\mathrm{import}}}, \sigrets,\sigcloss \vdash_{\mathrm{comp-value}} c_{\mathrm{export}}}\\
  }{
    \vdash (\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss)
  }
\end{mathpar}

\subsection{Linking}
\label{sec:linking}

TODO:
\begin{mathpar}
  \inference{
  }{
    \var{comp}_1 \bowtie \var{comp}_2 = \var{comp}_3
  }
\end{mathpar}

@@

\[
  \comp{\scall{\offpc,\offsigma}{r_1}{r_2}} = 
  \begin{array}[t]{l}
    % Make the stack capability into the return capability and seal it:
    %   Push r_data to the stack (should this be made the responsibility of the programmer? If it happens here, then it should probably also be part of the call semantics. Especially, the call semantics should "eat" another piece of memory on the stack to make sure there is no discrepancy.)
    %   Seal the stack capability (with what? where does the seal come from? I think we talked about this, and it is something that should be handled like linking (a fresh seal is available in the beginning of a programs code along with a capability for a linking table)).
    % restrict the stack capability to the unused part (and clear this part (is this really necessary?)).
    % make return capability and ceal it:
    %   Move a copy of pc to a different register.
    %   Adjust the pc copy to point to the return address.
    %   Seal it with the seal.
    % remove all data from temp registers (that is at least the seal).
    % jmpx to r1 and r2
    % restore code:
    %   check the stack end address.
    %   move the stack pointer to the proper register
    %   pop the data capability
  \end{array}
\]

@@

\[
  \codereg{\ta,\sigrets,\sigcloss} \defeq (\pure,*,=,=,H^\mathrm{code} \; \ta \; \sigrets \; \sigcloss \; \code,H^\mathrm{code}_\sigma \; \ta \; \sigrets \; \sigcloss \; \code)
\]

\begin{equation*}
  H^\mathrm{code} \; \ta \; \sigrets \; \sigcloss \; \code \; s \; \hat{W} = \left\{\npair{(\code,\code)} \middle|
    \dom(\code) = [\aaddr,\baddr]
  \right\}
\end{equation*}

\lau{19-03-2018: Add the link capability to the above? code in ta?}
\begin{multline*}
  H^\mathrm{code}_\sigma \; \ta \; \sigrets \; \sigcloss \; \code \; s \; \sigma \; \hat{W} = \\
  \begin{array}[t]{l}
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\retptrc(\rx,\lin,\baddr,\eaddr,\aaddr'+\calllen - 1),\\((\rx,\lin),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \decInstr{\code([a',a' + \calllen-1])} = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}} \tand \\
        \aaddr = \aaddr' + \retoffset \tand \\
        \code(a+\offpc) = \seal{\sigma_b,\sigma_e,\_} \tand \sigma = \sigma_b + \offsigma \in \sigrets \tand\\
        \lbrack \baddr, \eaddr \rbrack \subseteq \dom(\code) \subseteq \ta
      \end{array}
    \end{array}
      \right\} \uplus \\
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\retptrd(\baddr,\eaddr),\\((\rw,\linear),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \exists r \in \dom(\pwpriv[\xi(\hat{W})]) \ldotp \pwpriv[\xi(\hat{W})](r) \nequal (\stareg[(\ms,\ms)]{\spa}, ((\rx,\lin),\baddr',\eaddr',\aaddr'+\calllen)) \tand \\
        \quad \dom(\ms) = [\baddr,\eaddr] \tand\\
        \quad \decInstr{\code([a',a' + \calllen-1])} = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}} \tand \\
        \quad \code(a+\offpc) = \seal{\sigma_b,\sigma_e,\_} \tand \sigma = \sigma_b + \offsigma \in \sigrets \tand\\
        \quad a = b-1\tand \\
        \quad \lbrack \baddr', \eaddr' \rbrack \subseteq \dom(\code) \subseteq \ta
      \end{array}
    \end{array}
      \right\} \uplus\\
    \left\{
    \begin{array}{l}
\left. \npair{(\vsc, \vsc' )} \middle| \right. \\
      \begin{array}{l}
        \sigma \in \sigcloss \tand\\
        (\dom(\code) \mathrel{\#} \ta \tand \npair{(\vsc,\vsc')} \in \lrv \; W) \tor\\
        (\dom(\code) \subseteq \ta \tand \npair{(\vsc,\vsc')} \in \lrvtrusted \; W)
      \end{array}
    \end{array}
      \right\}
  \end{array}
\end{multline*}

@@

We want to make a conditional full-abstraction statement. The condition should express two things (1) the compilation so far has been reasonable, so we do not have to setup protection against things any reasonable compiler wouldn't do. (2) the compilation so far has taken care of certain checks that we do not have information to place correctly at this point of the compilation
\begin{definition}
  \label{def:check-stack-addr-before-call}
  A configuration $\src{\Phi}$ is said to have reasonable calls in $\ta$ for $n$ steps iff\\
  for all $i \leq n$ if
  \[
    \src{\Phi} \nstep[i] \src{\Phi'}
  \]
  and $\src{\Phi'}$ points to $\src{\scall{\offpc,\offsigma}{r_1}{r_2}}$ in $A$ for some $\src{r_1}$ and $\src{r_2}$
  % and there exists no $j<i$ s.t.
  % \[
  %   \src{\Phi} \nstep[j] \src{\Phi''}
  % \]
  % where $\src{\Phi''}$ points to $\src{\scall{\offpc,\offsigma}{r_1'}{r_2'}}$ in $A$ for some $\src{r_1'}$ and $\src{r_2'}$,
  then
  \[
    \src{\Phi'}(\src{r_\stk}) = \src{\stkptr{\_,\stkb,\_,\_}}
  \]
  % and $\src{\Phi'}$ has reasonable calls in $A$ for $n-i$ step.
\end{definition}

\begin{definition}[Use return seals only for call]
  A configuration $\src{\Phi}$ is said to use linker seals properly in $\ta$ for $n$ steps iff\\
  for all $i \leq n$, if
  \[
    \src{\Phi} \nstep[i] \src{\Phi'}
  \]
  and $\src{\Phi'}$ points to $\src{\tcseal{r_1}{r_2}}$ in $\ta$ and $\Phi'(r_1) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$, then either $\src{\Phi'}$ is inside $\src{\scall{\offpc,\offsigma}{r_1'}{r_2'}}$ and $\sigma \in \sigrets$ or $\sigma \in \sigcloss$.
\end{definition}
